---
title: "STAT 250D Week 2 Activity"
author: "NAME"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---

# Activity: Exploratory Data Analysis

Run this code chunk before you start. You do not yet need to understand it.

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(mosaic)
library(ggformula)
```

## Part 1: Penguins data

Read in the `penguins.csv` data set and print the variable names.  

```{r}
#| label: import-penguin-data

penguins <- ___goal___("___filename___")
___goal___(penguins)
```

### 1.1

Let's recreate the graphic on page 2-23 of your course notebook, a histogram of bill depth for each penguin species with a bin width of 0.3mm. Before writing the actual R code, identify each of the following pieces of our generic code template.  

`goal(formula,...)`  


a.  `goal`: Identify the goal. What do you want R to do? Describe the goal in words and then write the function name as you would type it in R.  

> Insert answer here  


b.  `formula`: Identify the formula and the names of the variable(s) in the data set.  

> Insert answer here


c.  `...`: Identify any additional arguments you will use to create a good visualization.  

> Insert answer here  


Now, fill in the following code template with your answers from above to recreate the graphic on page 2-23 of your course notebook.  

```{r}
#| label: bill-depth-histogram

___goal___(___formula___, data=penguins,
           <insert additional arguments here>)
```

------------------------------------------------------------------------

#### Extra Practice Problems - continue to Part 2   

### 1.2.

Describe the **shape** (symmetry, modality) of the distribution of bill depth for *Gentoo* penguins.  

> Insert answer here  


### 1.3.

Here is the histogram of bill depth for all penguins. Describe its shape. Why do you think it is shaped the way it is? Justify your answer using the information in the histograms above (in question #1.1).  

```{r}
#| label: bill-depth-histogram-all

gf_histogram(~bill_depth_mm, data=penguins,
             xlab="Bill Depth (mm)",
             ylab="Number of Penguins",
             title="Penguins in the Palmer Archipelago",
             binwidth = 0.3)
```

> Insert answer here  


### 1.4.

Describe the distribution of bill depth for the other two species (Adelie, Chinstrap). Compare the bill depth between species.  

> Insert answer here  


### 1.5.

Do you think you could identify a penguin's species from its bill depth alone? Explain why or why not.  

> Insert answer here  


## Part 2: King County data

Recall the King data set that represents a sample of babies born in 2001 in King County, Washington. We are going to explore the following research question:

On average, did women in King County, Washington with different educational levels have babies with different birth weights in 2001?

```{r}
#| label: import-king-data

king <- read.csv("king.csv")

# This line of code reorders education levels as low, middle, high - you DO NOT yet need to understand until later in the semester
king <- mutate(king, educlv = factor(educlv, levels=c("Low","Middle","High"))
```


### 2.1.

Create a histogram that addresses the question, being sure to use good graphic practices.

< Insert code chunk >


### 2.2.

Calculate summary statistics of birth weight for each education level.

< Insert code chunk >


------------------------------------------------------------------------

#### Extra Practice Problems  

### 2.3.

Describe the shape of each distribution. Based on the shape, how do you expect the mean and median birth weight to compare for each education level? Why?  

> Insert answer here  


### 2.4.

Compare the mean and median birth weight for each education level. If any, how large are the differences between the mean and median? Are these differences meaningful?  

> Insert answer here  


### 2.5.

Determine if there are any outliers of birth weight for mothers with *high* education levels. If so, how many are there? Are they unusually large or unusually small birth weights? How do you know?  

< Insert code chunk >

> Insert answer here  


